### 2025-01-21 paper/icml25/first/sects/experiments.tex
fix

\paragraph{Transport}
The third row of \Cref{fig:experiments} presents a differentiable scenario, transport. In the first column (single agent), PPO fails to converge, while SHAC and \fname{} achieve comparable performance. \fname{} converges faster, but SHAC is more consistent due to direct gradient stability. In the second and third columns (3 and 5 agents), PPO fails to converge, while SHAC and \fname{} both complete the task around 10,000 episodes. 
With more agents, convergence is faster because the task becomes easier (more agents can push the package).
The emergent of cooperation can be also display but looking to the gradient norm in \Cref{fig:grads-transformer-transport} we can see that the norm of the gradients for SHAC and \fname{} increases when the agents start to collide with each other and the package. This is a sign of generalization, as the agents learn to avoid collisions and push the package together.

>>>>

\paragraphTransport}
The third row of \Cref{fig:experiments} presents a differentiable scenario, transport. In the first column (single agent), PPO fails to converge, while SHAC and \fname{} achieve comparable performance. \fname{} converges faster, but SHAC is more consistent due to direct gradient stability. In the second and third columns (3 and 5 agents), PPO fails to converge, while SHAC and \fname{} both complete the task around 10,000 episodes. With more agents, convergence is faster because the task becomes easier (as more agents can push the package). The emergent of cooperation can be also display but looking to the gradient norm in \Cref{fig:grads-transformer-transport} we can see that the norm of the gradients for SHAC and \fname{} increases when the agents start to collide with each other and the package. This is a sign of generalization, as the agents learn to avoid collisions and push the package together.
